---
output: md_document
---

# Evaluation and Grading {-}

Much of the learning that you do in this course will be done at home. What this means, is that instead of applying what have learned in the classroom at home, working on a problem, writing a paper, etc., you will instead apply what you have learned at home, in the classroom. This is an effective way to learn the information because you are getting a chance to apply it right away. I will provide ample opportunity for you to apply in class what you have learned at home. This includes assignments, discussion participation, reading feedback (i.e., this reading was difficult because . . .). Each of these aspects will together comprise your grade in the course. Ultimately, what you learn, and the grade you will receive, will be up to you. You will get as much out of this course as you put in.

Your participation grade will be a cumulation of the points you've earned on each of the assignments, plus those points you earned through participation and attendance. The effect of this typically, is that if you are on the boarder between one grade you do not want, and a grade that you do, the attendance and participation will either bump your grade up, or leave it were it is.

Both attendance and participation are critically important aspects of this class. Just as important however, is reading the material *and take notes*! The class participation grade will be based on (a) attendance, (b) level of engagement during discussions and group exercises, (c) level of engagement on discord, and (d) the completion of other exercises.

Each of these elements is assigned a point value and assessed using a scale that awards full, partial, or no credit. This scale is available to you at https://docs.google.com/spreadsheets/d/1g140Jx843x7aekG5fe8zyVbwymVSW8Rd-I3BX4VvqMI/edit?usp=sharing. If you click on the link, you can make a copy of and save the rubric to your own google drive account if you have one. If you do not, and you would still like to be able to calculate your own score on an assignment, it is easy to do. For each of the items on the rubric, e.g., "conclusion", I will assign a score between 1 and 4. If your conclusion on an assignment, for instance "ties up loose ends", but does not "consider obvious objections", I will give you a 3 rather than a 4 for the "conclusion item." Add up the scores that you received for each of the items, divide it by the possible total, depending on the rubric, either 12 or 40, and multiply that number by .1. This will give you the percentage, 100%, 85%, etc.

and:

<iframe style="width:100%; height:500px;overflow:auto;" src="https://docs.google.com/spreadsheets/d/1g140Jx843x7aekG5fe8zyVbwymVSW8Rd-I3BX4VvqMI/pubhtml?gid=0&amp;single=true&amp;widget=true&amp;headers=false"></iframe>

Then look at the course grading scale and this will tell you what letter grade you earned on that assignment.

```{r, echo=FALSE}
points <- data.frame(
  Assignment = c("Participation", "Weekly Discussion Preps", "Mini Argument", "Problem Collaboration", "Final Project"),
  Points = c("10 pts", "6 pts", "30 pts", "35 pts", "410 pts"),
  Quantity = c("x10", "x15", "x5", "x8", "x1"),
  Total = c("100 pts", "60 pts", "150 pts", "280 pts", "410 pts"),
  Percent = c("10%", "6%", "15%", "28%", "41%"),
  stringsAsFactors = FALSE
)

knitr::kable(
  points, booktabs = TRUE,
  caption = "PHI 240 Points Breakdown"
)
```



```{r, echo=FALSE}
grades1 <- data.frame(
  GPA = c("4.0", "3.7", "3.3", "3.0", "2.7"),
  Letter = c("A", "A-", "B+", "B", "B-"),
  Percent = c("93.0% - 100%", "90.0% - 92.9%", "87.0% - 89.9%", "83.0% - 86.9%", "80.0% - 82.9%"),
  stringsAsFactors = FALSE
)

grades2 <- data.frame(
  GPA = c("2.3", "2.0", "1.7", "1.0", "0.0"),
  Letter = c("C+", "C", "C-", "D", "F"),
  Percent = c("77.0% - 79.9%", "73.0% - 76.9%", "70.0% - 72.9%", "63.0% - 69.9%", "< 63.0%"),
  stringsAsFactors = FALSE
)

knitr::kable(
  list(
    grades1,
    grades2
  ),
  caption = "Course Grading Scale", booktabs = TRUE
)
```

